\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV themes
\moderncvstyle{classic}                             % Style options: 'casual', 'classic', 'oldstyle', 'banking'
\moderncvcolor{blue}                                % Color options: 'blue', 'orange', 'green', 'red', 'purple', 'grey', 'black'
\renewcommand{\familydefault}{\sfdefault}           % Default font is the sans serif font

% Adjust the page margins
\usepackage[scale=0.85]{geometry}

% Personal data
\name{William}{Bell}
\address{10 Rogers Ave}{Somerville, MA 02144}{}
\phone[mobile]{(662)~610~0467}
\email{wjbell97@gmail.com}

% Content
\begin{document}

\makecvtitle

\section{Summary}
An enthusiastic engineer with diverse experience who is driven to boost colleagues' productivity with better tools.

\section{Experience}
\cventry{Jun 2023 -- Present}{Software Engineer}{MathWorks}{}{}{
  \begin{itemize}
    \item Develop cloud-native tools, infrastructure, and applications for MathWorks developers and customers.
    \item Contribute code and infrastructure changes to ensure observability, high-availability, and scalability.
    \item Ensure quality at all levels of testing ranging from functional to non-functional and unit to integration to scalability.
    \item Maintain observability and alerts for Service Level Objectives (SLOs) by implementing Prometheus metrics and Grafana dashboards.
    \item Implement and maintain CI/CD pipelines to automate software delivery processes.
    \item Collaborate with cross-functional teams to deliver high-quality software products.
  \end{itemize}
}
\cventry{Mar 2022 -- Jun 2023}{Application Support Engineer}{MathWorks}{}{}{
  \begin{itemize}
    \item Completed project rotations with various teams, including robotics toolboxes, ROS Toolbox, and IoT products such as ThingSpeak.
    \item Supported MathWorks' code generation products and contributed to development teams in the MATLAB Online group.
    \item Assisted customers in using code generation technologies and provided technical support.
    \item Gained experience in Go, TypeScript, IoT, code generation, C/C++, and MATLAB.
  \end{itemize}
}
\cventry{May 2021 -- Jan 2022}{Intern}{MathWorks}{}{}{
  \begin{itemize}
    \item Augmented trajectory optimization capabilities for differentially flat systems in the Navigation and UAV Toolboxes.
    \item Evaluated various third-party quadratic and nonlinear solvers for robotics applications.
  \end{itemize}
}
\cventry{Jun 2019 -- May 2021}{Aerospace Engineer}{Dynetics, Inc.}{}{}{
  \begin{itemize}
    \item Co-owned a company-wide library of simulation and control tools written in Python.
    \item Designed and implemented path planning and collision-avoidance algorithms for UAV route planning software.
    \item Implemented state-of-the-art reinforcement learning algorithms and other machine learning techniques.
  \end{itemize}
}

\section{Education}
\cventry{2019}{Bachelor of Science}{Mississippi State University}{Aerospace Engineering}{}{}
\cventry{2021}{Master of Science}{Boston University}{Robotics and Autonomous Systems}{}{}

\section{Skills}
\cvitem{Languages}{Go, Python, TypeScript, C/C++}
\cvitem{Cloud}{AWS, Kubernetes, Containerization}
\cvitem{Observability}{Prometheus, OpenTelemetry, Grafana, Jaeger, Splunk}
\cvitem{Quality}{Go test packages (e.g. \texttt{testing}, \texttt{testcontainers}), k6 load-testing, TeamCity CI/CD}

\end{document}
